%!tex program=xelatex
%!tex root=main.tex
% مراجع خود را در این قسمت وارد کنید
\begin{thebibliography}{47}
\addcontentsline{toc}{chapter}{\numberline{~}مراجع}
% چنانچه مرجع فارسی هم دارید باید دستور زیر را فعال کرده و مراجع فارسی خود را بعد از این دستور وارد کنید
%\persian
%\bibitem{11} 
%آذرپناه, فریبرز, نخستین درس در توپولوژی, انتشارات دانشگاه شهید چمران اهواز, %1382
%\bibitem
% بهبودی، محمود، پایان نامه دکتری، انتشارات دانشگاه شهید چمران اهواز, 1382
\latin
\LTRbibitems
%\baselineskip=3.5ex

\bibitem{a-r}
Albu, T., Rizvi, S. (2001). Chain conditions on quotient finite dimensional mod-
ules.Comm. Algebra 29 (5): 1909-1928

\bibitem{al-sm-2}
Albu, T., and Smith, P. F., {\it Localization of modular lattices, Krull dimension, and the Hopkins-Levitzki Theorem (I)},
Math. Proc Cambridge Philos Soc. 120 (1996), 87-101.

\bibitem{al-sm-3}
Albu, T., and Smith, P. F., {\it Localization of modular lattices, Krull dimension, and the Hopkins-Levitzki Theorem (II)}, Comm. Algebra 25 (1997), 1111-1128.

\bibitem{al-sm}
Albu, T., and Smith, P.F., {\it Dual Krull dimension and duality}, Rocky Mountain J.Math. 29 (1999), 1153-1165.

\bibitem{al-t1p}
Albu, T., and Teply, L., {\it Generalized deviation of posets and modular lattices}, Discrete Math. 214 (2000), 1-19.

\bibitem{al-va}
Albu, T., and Vamos, P., {\it Global Krull dimension and global dual Krull dimension of valuation rings}, Lecture Notes in Pure and Applied Mathematics. Vol 201 (1998), 37-54.


\bibitem{an-fu}
Anderson, F.W., and Fuller, K.R., {\it Rings and categories of modules}, Springer-Verlag, 1992.

\bibitem{ar1}
Armendariz, P., {\it Rings with an almost Noetherian ring of fractions}, Math. Scand. 41 (1977), 15-18

\bibitem{1}
Atiyah, M., MacDonald, I.G., {\it Introduction to Commutative Algebra}, Addison-Wesley, London, 1969.


\bibitem{bass}
Bass, H., {\it Descending chains and the Krull ordinal of commutative rings}, J.
Pure Appl. Algebra 1: 347--360.


\bibitem{b-g}
Bilhan, G., and Gungoroglu, T., {\it w-coatomic modules}, Cank. Uni. J. Eng. 7(2010),No1. 17-24.

\bibitem{b-h}
Bilhan, G., and Hatipoglu, C., {\it Finitely coatomic modules}, Hacet. J. Math. Stat. 36(2007), 37-41. 

\bibitem{b-s}
Bilhan, G., and Smith, P.F., {\it Short modules and almost Noetherian modules}, Math. Scand. 98 (2006), 12-18.

\bibitem{camilo}
 Camillo, V. P., and Zelmanowitz, J., {\em On the dimension of a sum of modules}, Comm. Algebra, 6(1978), no 4, 345-352.

\bibitem{ch}
Chambless, L., {\it N-Dimension and N-critical modules, Application to Artinian
modules}, Comm. Algebra 8 (1980), 1561-1592.

\bibitem{co1}
Cohen, I., {\it Commutative rings with restricted minimum condition}, Duke Math. J. 17 (1950), 27-42.

\bibitem{c-l}
Croisot, R., Lesieur, L., {\it Sur les anneaux premier a gauch}, Ann. sci. E'col. Norm. sup, 79(1959), 161-183.

\bibitem{d-f}
Dauns, J., Fuchs, L., {\it Infinite Goldie dimension}, J. Algebra, 115, (1983), 247-302.

\bibitem{d-k}
Davoudian, M., Karamzadeh, O. A. S., 
{\it Artinian serial modules over commu-
tative (or left Noetherian) rings are at most one step away from being Noetherian.}
Comm. Algebra, to appear.

\bibitem{d-k-sh} 
Davoudian, M., Karamzadeh, O. A. S., Shirali, N., {\it On $\alpha$-short modules}, to appear. 

\bibitem{dung}
Dung, N. V., Huynh, D. V., Smith, P. F., and Wisbauer, R., {\em Extending Modules}, Longman, Harlow, 1990.

\bibitem{fu}
Fuchs, L., {\it Torsion preradical and ascending Loewy series of modules},
J. Reine und Angew. Math. 239 (1970), 169-179.

\bibitem{g1}
Goldie, A.W., {\it The structure of prime rings under ascending chain conditions}, Proc. London Math. soc. VIII(1958), 589-608.

\bibitem{g1}
Goodearl, K.R., {\it Von Neumann ergular rings}, Pitman, san, Francisco, 1979.

\bibitem{g2}
Goodearl, K.R., Warfield, JR. R. B., {\it An Introduction to Noncommutative Noetherian rings}, Cambridge University Press, 1989.

Goodearl, K. R., Zimmermann-Huisgen, B. (1986). Lengths of submodule chain
versus Krull dimension in Non-Noetherian modules. Math. Z. 191: 519-527.

Gordon, R. (1974). Gabriel and Krull dimension, in : Ring Theory (Proceeding of
the Oklahoma Conference), Lecture Notes in Pure and Appl. Math. Vol. 7: Dekker,
NewYork pp. 241-295.

\bibitem{go-ro}
Gordon. R., and Robson, J.C., {\it Krull dimension}, Mem. Amer. Math. Soc. 133, 1973.
 
\bibitem{gu1}
Gungoroglu, G. {\it Coatomic modules}, Far East J. Math. Sci. Special Volume (1998), part  II, 153-162

\bibitem{kh}
Hashemi, J., Karamzadeh, O.A.S., and Shirali, N., {\it Rings over
which the Krull dimension and the Noetherian dimension of all
modules coincide}, Comm. Algebra 37 (2009), 650-662.

\bibitem{h1}
Hein, J., {\it Almost Artinian modules}, Math. Scand. (1979) 198-204.

\bibitem{hi}
Hirano, Y., {\it On rings over which each modules has a maximal submodule}, Comm. Algebra 26 (1998), 3435-3445.

\bibitem{ka1}
Karamzadeh, O.A.S., {\it Noetherian-dimension}, Ph.D. thesis, Exeter, 1974.

Karamzadeh, O.A.S. (1982) When are Artinian modules countable generated? Bull.
Iran. Math. Soc., 9, 171-176.
[14

\bibitem{ka5}
Karamzadeh, O.A.S., and Sajedinejad, A.R., {\it Atomic modules},
Comm. Algebra 2001, 29 (7), 2757-2773.

\bibitem{ka6}
Karamzadeh, O.A.S., and Sajedinejad, A.R., {\it On the Loewy length and the
Noetherian dimension of Artinian modules}, Comm. Algebra 30 (2002), 1077-1084.


\bibitem{ksh}
Karamzadeh, O.A.S., and Shirali, N., {\it On the countablity of Noetherian dimension of Modules}, Comm. Algebra 32 (2004), 4073-4083.


\bibitem{ka3}
Karamzadeh, O.A.S., and Motamedi, M., {\it On $\alpha$-$DICC$ modules},
Comm. Algebra 22 (1994), 1933-1944.

\bibitem{ka4}
Karamzadeh, O.A.S., and Motamedi, M., {\it a-Noetherian and Artinian modules},
Comm. Algebra 23 (1995), 3685-3703.


\bibitem{kas1} 
Kasch, F., {\it Modules and Rings}, London Mathematical Society Monographs, Vol. 17, Academic press, London 1982.


\bibitem{ki}
Kirby, D., {\it Dimension and length for Artinian modules}, Quart.
J. Math. Oxford. 41 (1990), 419-429.

\bibitem{kr}
Krause, G., {\it On fully left bounded left Noetherian rings}, J. Algebra 23 (1972), 88-99.

Krause, G. (1973). Descending chains of submodules and the Krull dimension of
Noetherian modules. J. Pure Appl. Algebra 3: 385-397.

\bibitem{le2}
Lemonnier, B., {\it D\'{e}viation des ensembles et groupes ab\'{e}liens
totalement ordonn\'{e}s}, Bull. Sc. Math. 96 (1972), 289--303.

\bibitem{le3}
Lemonnier, B., {\it Dimension de Krull et codeviation, Application au theorem d'Eakin}, Comm. Algebra 1978, 6, 1647-1665.

\bibitem{m1}
Matlis, E., {\it Modules with descending chain condition}, Trans. Amer. Math. Soc. 98(1960) 459-508.
	
\bibitem{m2}
Matlis, E., {\it Some properties of Noetherian domains of dimension one}, Canad. J. Math. 13 (1961) 569-586.

\bibitem{mc}
McConell, J.C., and Robson, J.C., {\it Noncommutative Noetherian Rings}, Wiley-Interscience, New York, 1987. 

\bibitem{puz}
Puczylowsky, E.R., {\it On the uniform dimension of the radical of a module}, Comm. Algebra 1995, 23(2), 771-776.

\bibitem{r-g}
Rentschler, P., and Gabriel, P., {\it Sur la dimension des anneaux et ensembles ordonn\'{e}s}, C. R. Acad. Sci. Paris 265 (1967), 712-715.

 \bibitem{ro}
Roberts, R.N., {\it Krull-dimension for Artinian Modules over
quasi local commutative Rings}, Quart. J. Math. Oxford. 26(1975),
269-273.

\bibitem{sa1}
Sarath, B., {\it Krull dimension and Noetherianess}, Illinois J. Math., 20(1976), 329-335.

\bibitem{13}
Sharp, R.Y., {\it Steps in Commutative Algebra}, Cambridge University Press, 1990.

\bibitem{Sharp2}
Sharp, R.Y., {\it A method for the study of Artinian modules with an application to asymptotic behavior}, Proceeding of micr-program(Commutative Algebra), Springer-Verlag, (1989), 443-464.

\bibitem{valle}
Valle, A., {\it Goldie dimension of a sum of modules}, Comm. Algebra 1994, 22(4), 1257-1269.

\bibitem{va1}
Vamos, P., {\it The dual of the notion of finitely generated}, J. London. Math. Soc,   43(1968), 643-646. 

\bibitem{w1}
Weakley, W. D., {\it Modules whose proper submodules are finitely generated}, J. Algebra, 84(1983), 189-219.

Wisbauer, R. Foundations of module and ring theory. Gordon and Breach, Philadel-
phia, 1991.

%%%\Persian
%\bibitem{smyth2}
%M.B. Smyth, Topology, S. Abramsky, D.M. Gabbay, T.S.E. Maibaum (Eds.), {\em Handbook of Logic in
%Computer Science}, Vol. 1, Clarendon Press, Oxford, 1992, pp. 641–761.
%\bibitem{topsze}
%F. Topsze, {\em Topology and Measure}, Lecture Notes in Mathematics, Vol. 133, Springer, Berlin, 1970.
\end{thebibliography}

